Component-Based mruby Platform for IoT Devices

### 2018-02-22 ipsj/paper.tex
Add sentences to related work
Fix evaluation

To demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.

@@

The development using GPLs such as C, JavaScript, Python, and Android allows the extremely efficient systems based on the complete control over individual devices.
However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.

The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
In addition, the extended mruby on TECS supports legacy code such as a motor driver.
mruby has the same syntax as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.

>>>>

Next, to demonstrate the low overhead of TINET+TECS, we compared its execution time and memory consumption with that of TINET, producing the results shown in Fig. \ref{fig:EvaluationOfExecutionTime}.

@@

The development using GPLs such as C, JavaScript, Python, and Android allows the extremely efficient systems based on the complete control over individual devices.
However, GPLs need more development effort, and it is difficult to reuse software due to platform-dependent design.
Several Open-source runtime systems for scripting languages have been proposed such as python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}.
mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
That is, mruby programs can be executed at the same speed as C, which is faster than other scripting languages.

The proposed framework can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
Therefore, the proposed framework can reduce memory consumption.
In addition, the extended mruby on TECS supports legacy code such as a motor driver.
mruby has the same syntax as Ruby which has advantages to web application development as it uses in Rails framework \cite{url:rubyonrails}.
